---
title: "NYC Airbnb"
author: "Jeff Goldsmith"
date: "10/9/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

## Data import

I'll load the tidyverse and the dataset. I'm also doing a bit of editing and renaming to make my life easier. 

```{r}

```

## Understanding variables

Next I'll do a bit of inspection to make sure I understand the data structure.

```{r}

```

## Brainstorming questions

### Does rating vary by neighborhood, room type, or both?

First I'll create a table to look at rating by boro.

```{r}

```

Next I'll try some visual displays.

```{r}

```

Finally, I'm interested in the `room_type` variable. Rating didn't seem to vary much across this variable, but I'd still like to examine this and boro at the same time. 

The chunk below creates a table, and then uses `knitr::kable()` to format the output.

```{r}

```

### Do hosts with more listings have higher or lower ratings?

First I'll look at the number of properties by each host. This code gave me some trouble in class -- the first try and the better approach are both shown below. 

```{r}

```

We'll use `calculated_host_listings_count` moving forward for this question -- that gives the total number of rentals that are hosted by the host in the row. 

I'll try to answer this using a scatterplot

```{r}

```

I'll also try to answer this using a numeric summary for a binary `lots_of_houses` variable.

```{r}

```

If anything, hosts with lots of apartments have slightly lower ratings. 

### Where are rentals located?

I'm going to use [latitude](https://en.wikipedia.org/wiki/Latitude) and [longitude](https://en.wikipedia.org/wiki/Longitude) to plot the location of rentals. I always get lat and mixed up, and it seems like the person who put these data together did as well ...

```{r}

```

Next I'll try to clean this up a bit and use other aesthetic mappings. For simplicity, I'll also focus on Manhattan.

```{r, fig.asp = 1}

```

We can learn quite a bit from this -- there are fewer rentals in some neighborhoods of Manhattan than others, and there seems to be a slight decrease in rating for rentals farther north than downtown. 

### Other questions

There are several questions we didn't get to:

* How is price related to other variables?
* How are descriptions related to number of reviews?
* Which rentals make the most money?
* What's different about low-availability rooms?

Of these, the question dealing with descriptions is one we're not in a position to handle yet -- that involves parsing character strings, which we'll get to shortly. The others we could at least explore using the tools we have at our disposal now.
